A Horrocks-type theorem for even orthogonal $K_2$

### 2020-06-19 horrocks.tex
Minor fix
Final version with integrated bibliography

%
%-----------------headlines-----------------------------------
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}

@@

\def\LOCAL{\horrocks.files}

\addbibresource{horrocks.files/references.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}
\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}

@@

\begin{document}
%%%%% ------------- fill in your data below this line  -------------------
%%%%%    The following lines \Title ... \EndAddress must ALL be present
%%%%%    and in the given order.
\Title
A Horrocks-type theorem for even orthogonal $K_2$
\ShortTitle 
A Horrocks-type theorem for $\mathrm{KO}_2$ 
\SubTitle   
%%%%%    A possible subtitle goes here.
\Author 
Andrei Lavrenov, Sergey Sinchuk
\ShortAuthor 
Lavrenov and Sinchuk
\EndTitle
\Abstract 
We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups. The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
\EndAbstract
\MSC 
19C20
\EndMSC
\KEY 
Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
\EndKEY
%%%%%    All 4 \Address lines below must be present. To center the last
%%%%%    entry, no empty lines must be between the following \Address
%%%%%    and \EndAddress lines.
\Address
Andrei Lavrenov
avlavrenov@gmail.com
\Address
Sergey Sinchuk
sinchukss@gmail.com
\Address
Chebyshev laboratory, 
St. Petersburg State University, 
14th. Line V.O. 29b
199178, St. Petersburg, Russia
\Address
\EndAddress
%%
%%       Make sure the last tex command in your manuscript
%%       before the first \end{document} is the command  \Addresses
%%
%%---------------------Here the prologue ends---------------------------------
%%--------------------Here the manuscript starts------------------------------

%%--------------------Here the manuscript ends--------------------------------
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

@@

\begin{externaltheorem}[Stein] \label{thm:Stein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}

@@

Let us fix some relation $R = [x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$. We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
Without loss of generality we may assume $e \geq d$ and $e > 0$. We need to consider two cases.
\begin{enumerate}
\item In the case $0 < d \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
\newline
\scalebox{0.84}{\begin{minipage}{1.16\linewidth}
\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \nonumber \\ 
 = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_1 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
 = {}^{x_{-\beta}(t^d)} [x_{\gamma}(- bt^e), x_{\alpha+\beta}(-\delta_1 \cdot a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
 = {}^{x_{-\beta}(t^d)} [x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \nonumber \\ 
 = [x_{\gamma}(bt^e) \cdot x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \nonumber \\ 
 = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
 = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \label{first-computation} \end{align}\end{minipage}} \vskip \belowdisplayshortskip
 where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.

\item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
\newline \scalebox{0.85}{\begin{minipage}{1.16\linewidth}
\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
 = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
 = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
 = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
 \end{enumerate}

@@

\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has $j_R^{-1}(p_1) \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
\begin{proof} 
By our assumption of the injectivity of $j_R$ and the above discussion the preimage $j_R^{-1}(p_1)$ consists of only one element, so the statement of the lemma is unambiguous.

>>>>

%
%-----------------headlines-----------------------------------
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{filecontents}

@@

\def\LOCAL{\horrocks.files}
\begin{filecontents}{horrocks.bib}
@Article{Abe83,
    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
    Author = {Abe, Eiichi},
    Journal = {Comm. Alg.},
    Year = {1983},
    Number = {12},
    Pages = {1271-1307},
    Volume = {11},
    Doi = {10.1080/00927878308822906} }

@book{BHS11,
    title = {Nonabelian algebraic topology},
    author = {Brown, Ronald and Higgins, Philip J. and Sivera, Rafael},
    series = {EMS Tracts in Mathematics},
    volume = {15},
    year = {2011} }

@book{HOM,
    Title = {The classical groups and $K$-theory},
    Author = {Hahn, Alexander J. and O'Meara, Timothy},
    Year = {1989},
    Publisher = {Springer} }

@Article{Ka77,
    Title = {Another presentation for {S}teinberg groups},
    Author = {Kallen, Wilberd van der},
    Journal = {Indag. Math.},
    Volume = {80},
    Number = {4},
    Pages = {304--312},
    Year = {1977},
    Doi = {10.1016/1385-7258(77)90026-9} }

@Book{Lam10,
    Title = {Serre's problem on projective modules},
    Author = {Lam, Tsit-Yuen},
    Publisher = {Springer Science \& Business Media},
    Year = {2010},
    Doi = {10.1007/978-3-540-34575-6} }

@online{La15,
    Title = {Local-global principle for symplectic $K_2$},
    Author = {Lavrenov, Andrei},
    Year = {2015} }

@Article{LS17,
    Title = {Centrality of odd orthogonal $K_2$},
    Author = {Lavrenov, A. and Sinchuk, S.},
    Journal = {J. Pure Appl. Alg.},
    Volume = {221},
    Year = {2017},
    Pages = {1134--1145},
    url = {https://arxiv.org/pdf/1606.00272.pdf} }

@Inproceedings{RS76,
    Title = {Finitely presented groups of matrices},
    Author = {Rehmann, Ulf and Soul{\'e} , Christophe},
    Booktitle = {Algebraic K-Theory},
    Publisher = {Springer},
    Year = {1976},
    Pages = {164--169},
    Series = {Lect. Notes. Math.},
    Volume = {551},
    Doi = {10.1007/BFb0079999} }

@Article{S15,
    Title = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },
    Author = {Sinchuk, Sergey},
    Journal = {J. Pure Appl. Alg.},
    Year = {2016},
    Number = {2},
    Pages = {857--875},
    Volume = {220},
    Doi = {10.1016/j.jpaa.2015.08.003} }

@Article{St-poly,
    Title = {Homotopy invariance of non-stable $K_1$-functors},
    Author = {Stavrova, Anastasia},
    Journal = {J. K-th.},
    Year = {2014},
    Number = {2},
    Pages = {199--248},
    Volume = {13},
    Doi = {10.1017/is013006012jkt232} }

@Article{St-serr,
    Title = {Non-stable $K_1$-functors of multiloop groups},
    Author = {Stavrova, Anastasia},
    Journal = {Canad. J. Math.},
    Year = {2014},
    Doi = {10.4153/CJM-2015-035-2} }

@Book{St67,
    Title = {Lectures on Chevalley groups},
    Author = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
    Year = {1967},
    Publisher = {Yale Univ. New Haven}}

@Article{Ste73,
    Title = {Surjective stability in dimension 0 for $K_2$ and related functors},
    Author = {Stein, Michael R.},
    Journal = {Trans. Amer. Math. Soc.},
    Year = {1973},
    Pages = {165--191},
    Volume = {178},
    Doi = {10.2307/1996696} }

@Article{Su77,
    Title = {On the structure of the special linear group over commutative rings},
    Author = {Suslin, Andrei},
    Journal = {Math. USSR Izv.},
    Year = {1977},
    Pages = {221--238},
    Volume = {11},
    Doi = {10.1070/IM1977v011n02ABEH001709} }

@Article{Tu83,
    Title = {The {S}teinberg group of a polynomial ring},
    Author = {Tulenbaev, Marat},
    Journal = {Math. USSR Sb.},
    Year = {1983},
    Pages = {131--144},
    Volume = {45},
    Doi = {10.1070/SM1983v045n01ABEH002591} }

@Article{ST76,
  author    = {Suslin, Andrei and Tulenbaev, Marat},
  title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
  journal   = {J. Soviet Math.},
  year      = {1981},
  volume    = {17},
  number    = {2},
  pages     = {1804-1819},
  doi       = {10.1007/BF01091768}}

@Book{Kbook,
    Title = {The $K$-book: An introduction to algebraic $K$-theory},
    Author = {Weibel, Charles A},
    Volume = {145},
    Year = {2013},
    Publisher = {Amer. Math. Soc.},
    Series = {Grad. Texts Math.} }

@Article{Vav09,
    Title = {Weight elements of Chevalley groups},
    Author = {Vavilov, Nikolai A.},
    Journal = {St. Petersburg Math. J.},
    Year = {2009},
    Number = {1},
    Pages = {23--57},
    Volume = {20},
    Doi = {10.1090/S1061-0022-08-01036-4} }

@Article{We14,
    Title = {On homology of linear groups over $k[t]$},
    Author = {Wendt, Matthias},
    Journal = {Math. Res. Lett.},
    Year = {2014},
    Number = {6},
    Volume = {21},
    Doi = {10.4310/MRL.2014.v21.n6.a15} }

@Article{Ma69,
    title = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
    author = {Matsumoto, H.},
    journal = {Ann. Sci. ENS},
    year = {1969},
    number = {1},
    pages = {1--62},
    volume = {2},
    url = {http://eudml.org/doc/81843} }

@article{AF17,
    title = {An explicit KO-degree map and applications},
    author = {Asok, Aravind and Fasel, Jean},
    doi = {10.1112/topo.12007},
    volume = 10,
    Issue = 1,
    Year = 2017,
    Pages = {268-300},
    Journal = {J. Top.} }

@article{Ste13,
    author = {Stepanov, A.},
    title = {Elementary calculus in Chevalley groups over rings},
    journal = {J. Prime Res. Math.},
    volume = {9},
    year = {2013},
    pages = {79--95},
    url = {http://alexei.stepanov.spb.ru/papers/errors.pdf} }

@article{Sch16,
    author = {Schlichting, Marco},
    title = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
    year = 2017,
    volume = 221,
    Issue = 7,
    Pages = {1729--1844},
    Doi = {10.1016/j.jpaa.2016.12.026},
    Journal = {J. Pure Appl. Alg.} }

@article{FRS12,
    title = {On stably free modules over affine algebras},
    author = {Fasel, Jean and Rao, Ravi and Swan, Richard},
    Volume = 116,
    Issue = 1,
    Pages = {223--243},
    Year = 2012,
    Journal = {Publ. Math. IH{\'E}S},
    doi = {10.1007/s10240-012-0041-y} }

@article{Lo78,
    author = {Loday, Jean-Louis},
    journal = {J. Alg.},
    title = {Cohomologie et groupes de Steinberg relatifs},
    year = {1978},
    volume = {54},
    number = {1},
    doi = {10.1016/0021-8693(78)90025-X},
    pages = {178--202} }

@article{Pa89,
    author = {Panin, Ivan},
    title = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
    journal = {Leningrad Math. J.},
    year = {1990},
    volume = {1},
    number = {3},
    url = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf},
    pages = {741--754} }

@article{Ka80,
    title = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
    author = {Karoubi, Max},
    journal = {Ann. Math.},
    volume = {112},
    number = {2},
    pages = {259--282},
    year = {1980},
    doi = {10.2307/1971147} }

@article{Hur77,
    author = {Hurrelbrink, J{\"u}rgen},
    title = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
    journal = {Math. Ann.},
    volume = {225},
    year = {1977},
    number = {2},
    pages = {123--129},
    doi = {10.1007/BF01351716} }

@online{Re75,
    title = {\href { http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf } { Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$ }},
    author = {Rehmann, Ulf},
    year = {1975} }

@article{MR91,
    title = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
    author = {Morita, Jun and Rehmann, Ulf},
    journal = {Math. Z.},
    volume = {206},
    number = {1},
    pages = {57--66},
    year = {1991},
    doi = {10.1007/BF02571324} }

@article{VP,
    year = {1996},
    journal = {Acta Appl. Math.},
    volume = {45},
    issue = {1},
    doi = {10.1007/BF00047884},
    title = {Chevalley groups over commutative rings: I. Elementary calculations},
    author = {Vavilov, Nikolai A. and Plotkin, E.},
    pages = {73--113} }

@article{St71,
    title = {Generators, relations and coverings of Chevalley groups over commutative rings},
    author = {Stein, Michael R},
    journal = {Amer. J. Math.},
    volume = {93},
    number = {4},
    pages = {965--1004},
    year = {1971},
    doi = {10.2307/2373742} }

@inproceedings{DS73,
    title = {The functor $K_2$: A survey of computations and problems},
    author = {Dennis, R Keith and Stein, Michael R},
    booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
    pages = {241--303},
    year = {1973},
    publisher = {Springer},
    doi = {10.1007/BFb0073728} }

@article{Ho05,
    title = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},
    author = {Hornbostel, Jens},
    journal = {J. Top.},
    volume = {44},
    number = {3},
    pages = {661--687},
    year = {2005},
    doi = {10.1016/j.top.2004.10.004} }

@Article{V00,
    title = {A third look at weight diagrams},
    author = {Vavilov, Nikolai A.},
    journal = {Rend. Sem. Mat. Univ. Padova},
    year = {2000},
    pages = {201--250},
    volume = {104},
    Url = {http://eudml.org/doc/108535} }

@article{A13,
    author = {Allcock, Daniel},
    title = {Steinberg groups as amalgams},
    journal = {Alg. Number Th.},
    year = {2016},
    volume = {10},
    number = {8},
    pages = {1791--1843},
    doi = {10.2140/ant.2016.10.1791} }

@article{Su82,
    title = {Quadratic modules and the orthogonal group over polynomial rings},
    author = {Suslin, A.~A. and Kopeiko, V.~I.},
    journal = {J. Soviet Math.},
    volume = {20},
    number = {6},
    pages = {2665--2691},
    year = {1982},
    doi = {10.1007/BF01681481} }

@article{Va86,
    author = {Vaserstein, L.},
    title = {On normal subgroups of Chevalley groups over commutative rings},
    journal = {Tohoku Math. J.},
    volume = {38},
    issue = {2},
    pages = {219--230},
    year = {1986},
    doi = {10.2748/tmj/1178228489} }

@online{VZ18,
    author = {Vavilov, Nikolai A. and Zhang, Zuhong},
    title = {Generation of relative commutator subgroup in Chevalley groups, II},
    archivePrefix = "arXiv",
    eprint = "1811.11263",
    primaryClass = "math.GR",
    year = {2018} }

@article{St-Ded,
    author = {Stavrova, Anastasia},
    title = {Chevalley groups of polynomial rings over Dedekind domains},
    journal = {J. Gr. Th.},
    volume = {23},
    issue = {1},
    doi = {10.1515/jgth-2019-0100},
    year = {2020}}

@article{Das17,
    title = {$\mathbb{P}^1$-gluing for local complete intersections},
    author = {Das, Mrinal Kanti and Tikader, Soumi and Zinna, Md Ali},
    journal = {Math. Z.},
    pages = {1--19},
    year = {2017},
    doi = {10.1007/s00209-019-02299-5} }

@article{Su76,
    title = {Projective modules over polynomial rings are free},
    author = {Suslin, Andrei},
    journal = {Dokl. Akad. nauk SSSR},
    volume = {229},
    pages = {1063--1066},
    year = {1976},
    url = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} }

@article{Qu76,
    author = "Quillen, Daniel",
    title = "Projective modules over polynomial rings",
    journal = "Inv. Math.",
    year = "1976",
    volume = "36",
    number = "1",
    pages = "167--171",
    doi = "10.1007/BF01390008" }

@article{Ho64,
    title = {Projective modules over an extension of a local ring},
    author = {Horrocks, Geoffrey},
    journal = {Proc. London Math. Soc.},
    volume = {3},
    number = {4},
    pages = {714--718},
    year = {1964},
    doi = {10.1112/plms/s3-14.4.714} }

@article{Mo04,
    title = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
    author = {Morel, Fabien},
    journal = {Comm. Math. Helv.},
    volume = {79},
    number = {4},
    pages = {689--703},
    year = {2004},
    publisher = {Springer},
    doi = {10.1007/s00014-004-0815-z} }

@article{St78,
    title = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},
    author = {Stein, M.~R.},
    journal = {Japan J. Math.},
    volume = {4},
    issue = {1},
    year = {1978},
    pages = {77--108},
    doi = {10.4099/math1924.4.77} }

@mastersthesis{Vo11,
    author = {V{\"o}lkel, Konrad},
    title = {\href { http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf } { Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie }},
    school = {Uni. Freiburg},
    year = {2011},
    type = {Diplomarbeit}}

@article{Ba74,
  title={Clifford algebras and spinor norms over a commutative ring},
  author={Bass, Hyman},
  journal={Amer. J. Math.},
  volume={96},
  number={1},
  pages={156--206},
  year={1974},
  doi={10.2307/2373586}}

@book{Bou81,
  title={Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
  author={Bourbaki, Nicolas},
  year={1981},
  publisher={Masson}}

@InProceedings{Ta86,
  Title                    = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},
  Author                   = {Taddei, Giovanni},
  Booktitle                = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
  Year                     = {1986},
  Pages                    = {693--710},
  Series                   = {Contemp. Math},
  Volume                   = {55},
  Url                      = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}

@article{La18,
  title={A local-global principle for symplectic $K_2$},
  author={Lavrenov, Andrei},
  year={2018},
  journal={Doc. Math.},
  volume={23},
  pages={653--675},
  doi={10.25537/dm.2018v23.653-675}}
\end{filecontents}

\addbibresource{horrocks.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}
\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}

@@

\begin{document}
%%%%% ------------- fill in your data below this line  -------------------
%%%%%    The following lines \Title ... \EndAddress must ALL be present
%%%%%    and in the given order.
\Title
A Horrocks-type theorem for even orthogonal $\mathrm{K}_2$
\ShortTitle 
A Horrocks-type theorem for $\mathrm{KO}_2$ 
\SubTitle   
%%%%%    A possible subtitle goes here.
\Author 
Andrei Lavrenov and Sergey Sinchuk
\ShortAuthor 
\EndTitle
\Abstract 
We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups. The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
\EndAbstract
\MSC 
19C20
\EndMSC
\KEY 
Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
\EndKEY
%%%%%    All 4 \Address lines below must be present. To center the last
%%%%%    entry, no empty lines must be between the following \Address
%%%%%    and \EndAddress lines.
\Address
Andrei Lavrenov
avlavrenov@gmail.com
\Address
Sergey Sinchuk
sinchukss@gmail.com
\Address
Chebyshev laboratory, 
St. Petersburg State University, 
14th. Line V.O. 29b
199178, St. Petersburg, Russia
\Address
\EndAddress
%%
%%       Make sure the last tex command in your manuscript
%%       before the first \end{document} is the command  \Addresses
%%
%%---------------------Here the prologue ends---------------------------------
%%--------------------Here the manuscript starts------------------------------

\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

@@

\begin{externaltheorem}[Stein] \label{thm:Stein} One has \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}

@@

Let us fix some relation $R = [x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$. We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
Without loss of generality we may assume $e \geq d$ and $e > 0$. We need to consider two cases.
\begin{enumerate}
\item In the case $0 < d \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = \hspace{4cm} \label{first-computation} \\ =
[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \nonumber \\ 
 = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_1 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
 = {}^{x_{-\beta}(t^d)} [x_{\gamma}(- bt^e), x_{\alpha+\beta}(-\delta_1 \cdot a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
 = {}^{x_{-\beta}(t^d)} [x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \nonumber \\ 
 = [x_{\gamma}(bt^e) \cdot x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \nonumber \\ 
 = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
 = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}
 where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.

\item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = \hspace{4cm} \\ = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
 = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
 = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
 = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}}\vskip \belowdisplayshortskip
where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
\end{enumerate}

@@

\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has 
\[j_R^{-1}(p_1) \cdot [p, h, u] = [p_1p, h, u].\] \end{lemma}
\begin{proof} 
By our assumption of the injectivity of $j_R$ and the above discussion the preimage $j_R^{-1}(p_1)$ consists of only one element, so the statement of the lemma is unambiguous.
